\documentclass{article}

% \email{r.mesquita@campus.fct.unl.pt}
% \homepage{alt-romes.github.io}
% \github{alt-romes}

\usepackage{hyperref}
\usepackage{geometry}
%\geometry{
%  a4paper,
%  left=20mm,
%  %right=
%  %bottom=
%  top=15mm}
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

\pagestyle{empty}

\usepackage{sectsty}
\sectionfont{\normalsize\sc\sectionrule{0pt}{0pt}{-5pt}{0.5pt}}

\newlength{\spacebox}
\settowidth{\spacebox}{123456789}
\newcommand{\sepspace}{\vspace*{1em}}

\newcommand{\name}[1]{\huge#1\normalsize\par\vspace*{0.5em}}

\newcommand{\info}[2]{
% set specific indentation for personal information
  \noindent\hangindent=2em\hangafter=0
% create a box to align two pieces of text
  \parbox{\spacebox}{%
  \textsl{#1}} % slanted entry name
  #2 \par} % entry value

% Skill
\newcommand{\skill}[2]{
\noindent\hangindent=2em\hangafter=0
\parbox{3\spacebox}{ \textsc{#1}} #2 \par}

% Simple Entry
% title, subtitle, right text, right subtext
\newcommand{\sientry}[4]{
  \noindent  \textbf{#1}
    \hfill \small #3 \normalsize \par
  \noindent \textit{#2}
    \hfill \small #4 \normalsize \par
}

% Line entry
\newcommand{\lientry}[3]{
\small
  \noindent \textbf{#1} #2 \hfill #3
\normalsize
}

\newcommand{\entry}[5]{
  \sientry{#1}{#2}{#3}{#4}
     \noindent\hangindent=2em\hangafter=0 \small #5
\normalsize \par
}


\begin{document}

\name{Rodrigo Mesquita}
\info{Email}{\texttt{rodrigo.m.mesquita@gmail.com}}
\info{Phone}{+351 937 771 064}
% \info{Site}{\texttt{alt-romes.github.io}}
% \info{Address}{Rua do Láparo 263 Q, 2890-551 Alcochete, Portugal}

% \section*{Summary}

\section*{Education}

  \entry
    {MSc. Computer Science and Engineering}
    {NOVA School of Science and Technology}
    {2018 - Today}
    {Lisboa, Portugal}
    {}
    % {Current average grade: 15.90}

\section*{Research}

  \entry
    {Typechecking Linearity in Core}
    {NOVA School of Science and Technology}
    {Oct. 2022 - Today}
    {Lisboa, Portugal}
    {The master thesis I'm working on concerns itself with typechecking
    linearity in Core such that optimizing transformations don't break syntatic
    linearity (which they currently do), and implementing it on GHC}

  \entry
    {Synthesis Of Linear Functional Programs}
    {NOVA School of Science and Technology}
    {Mar. 2021 - Jul. 2021}
    {Lisboa, Portugal}
    {I had the opportunity to be advised by Prof. Dr. Bernardo Toninho in
    writing this work, which was awarded the highest grade}

\section*{Work Experience}

  \entry
    {NOVA School of Science and Technology}
    {Teaching assistant}
    {Sept. 2022 - Jan. 2023}
    {Lisbon, Portugal}
    {
      \begin{itemize}
          \item {Teaching the practical course of Introduction to Programming in Python}
      \end{itemize}
    }

 \entry
    {Glasgow Haskell Compiler}
    {\href{https://gitlab.haskell.org/alt-romes}{Contributor}}
    {Feb. 2022 - Today}
    {Online, GHC}
    {
        \begin{itemize}
            \item {Making the Haskell AST GHC-independent following \emph{Trees
                that Grow} by Simon P.J. and Shayan Najd.}
            % \item {Running experiments on the internal representation of
            %     \emph{fast strings}.}
            \item {Drafting \emph{e-graphs} specialized to equality saturation
                for use in the pattern-match checker.}
            % \item {Improving the linear linter to successfully accept more
            %     optimized programs}
        \end{itemize}
    }

  \entry
    {Universität Koblenz}
    {Research assistant, guest lecturer}
    {Jun. 2022 - Aug. 2022}
    {Koblenz, Germany}
    {
      \begin{itemize}
          \item {Writing two modules to extend the course \emph{Introduction to Functional
              Programming}.}
          \item {Giving a guest lecture on the added modules.}
      \end{itemize}
    }

  \entry
    {Connektor}
    {Software developer (half-time)}
    {Feb. 2022 - Mar. 2022}
    {Lisboa, Portugal}
    {
      \begin{itemize}
        \item {Development of app to manage PATS (\emph{technical assistance
            requests in Portuguese})}
      \end{itemize}
    }

  \entry
    {Cult of Bits}
    {Software developer (internship)}
    {Nov. 2021 - Feb. 2022}
    {Lisboa, Portugal}
    {
      \begin{itemize}
        \item {Created a dashboard system for \emph{Efficio Consulting}}
        \item {Wrote a \href{https://github.com/alt-romes/cob-hs}{Haskell interface to the CoB platform}}
      \end{itemize}
    }

  \entry
    {Biofix}
    {Software developer (half-time)}
    {Sep. 2020 - May 2021}
    {Lisboa, Portugal}
    {
      \begin{itemize}
        \item {Development of a web-app for a salesforce to track their
            interactions.}
        % \item {Automated business-specific features using the CoB
        %     data-processing pipeline in Groovy.}
      \end{itemize}
    }

\section*{Relevant Projects}

  \lientry
    {\href{https://github.com/alt-romes/ghengin}{Ghengin}}
    {Shader centric, vulkan-based Haskell game engine, (ab)using
    \href{https://gitlab.com/sheaf/fir}{fir (by Sam Derbyshire)}}
    % {\textbf{+1} stars on GitHub}
    {2022 - 2023}

  \lientry
    {\href{https://github.com/alt-romes/hegg}{Hegg}}
    {Haskell e-graphs and equality saturation based on
    \href{https://dl.acm.org/doi/10.1145/3434304}{egg (POPL 2021)}}
    % {\textbf{+1} stars on GitHub}
    {2022}

  \lientry
    {\href{https://github.com/alt-romes/ghc-linear-synthesis-plugin}{GHC Linear Synthesis}}
    {A GHC plugin for synthesizing programs using bottom-up proof search in
    linear logic with focusing}
    % {\textbf{+1} stars on GitHub}
    {2022}

  \lientry
    {\href{https://github.com/alt-romes/c-compiler}{C compiler}}
    {which compiles C to LLVM; written in C}
    % {\textbf{+1} stars on GitHub}
    {2022}

  % \lientry
  %   {\href{https://github.com/alt-romes/operating-system}{Operating system}}
  %   {with a minimal libk, flat memory model, and paging (WIP)}
  %   % {\textbf{+2} stars on GitHub}
  %   {2021}

  % \lientry
  %   {\href{https://github.com/alt-romes/programmer-calculator}{Programmer calculator}}
  %   {-- a TUI calculator to work very close to the bits; written in C}
  %   % {\textbf{+163} stars on GitHub}
  %   {2021}

  \lientry
    {\href{https://github.com/alt-romes/gameboyemulator}{Gameboy emulator}}
    {which runs Tetris and passes the initial standard CPU and MBC1
    support tests; written in C}
    % {\textbf{+6} stars on GitHub}
    {2021}

  \lientry
    {\href{https://github.com/alt-romes/chip8-emulator-for-gameboy}{CHIP-8 emulator}}
    {that runs on a gameboy, written directly in gameboy assembly (RGBASM)}
    % {\textbf{+8} stars on GitHub}
    {2021}

\section*{Relevant Events}

  \lientry
    {ZuriHac}
    {-- a Haskell Hackathon where I got to chat and discuss ideas with brilliant
    people}
    % {\textbf{+8} stars on GitHub}
    {2022}

% \section*{Technical Skills}

%   \skill
%     {Fluent in}
%     {Haskell, C, Vim, Git, Java, HTML/CSS/JS, Portuguese, English}

%   \skill
%     {Conversational in}
%     {Python, \LaTeX, Assembly, Bash, German, Spanish}

%   \skill
%     {Know some}
%     {Swift, LLVM, Rust, Go, Erlang, Scala, Japanese, Russian}

\end{document}
